### Homework

1.  Do 5 CodeWars problems in R. Share your solutions here:

    ```{r}
    # 1
    mul <- function(a, b) {
      a * b
    }
    
    # 2
    solution <- function(number){
      sum <- 0
      for(i in 1:number-1) {
        if (i %% 15 == 0) {
          sum <- sum + i
        } else if (i %% 5 == 0) {
          sum <- sum + i
        } else if (i %% 3 == 0) {
          sum <- sum + i
        }
        }
      sum
    }
    
    # 3
    even_or_odd <- function(n) {
      if (n %% 2 == 0) {
        'Even'
      } else {
        'Odd'
      }
    }
    
    # 4
    get_count <- function(input_str){
      count <-0
      
      if (input_str == '') {
        count
      } else {
      
      for (i in 1:nchar(input_str)) {
        print(substring(input_str,i,i))
        if (grepl(substring(input_str,i,i), 'aeiou', fixed = TRUE) == TRUE) {
        count <- count + 1
      }
    }
      count
    }
    }
    
    # 5
    disemvowel <- function(string){
      gsub('[aeiouAEIOU]','',string)
     }

    ```

2.  Create a function that checks an input of type `int` and returns fizz if the number is a multiple of 3, buzz if the number is a multiple of 5, and fizzbuzz if the number is a multiple of 3 and 5.

    ```{r}
    fizzbuzz <- function(num) {
      output = ''
      if (num %% 3 == 0) {
        output <- paste(output, 'fizz')
      }
      if (num %% 5 == 0) {
        output <- paste(output, 'buzz')
      }
      output <- gsub(' ', '', output)
      output
    }
    
    print(fizzbuzz(15))

    ```

3.  **Mario Challenge:** In the classic Super Mario games, Mario ends each level by ascending a flight of stairs and leaping off the top to arrive at the castle at the end. (See [here](https://youtu.be/-avspZlbOWU?t=55) for details). We can imagine that each of the bricks of the stairs is a character X. Create a function that prints out a set of stairs. For example:

    If the function is called marioStairs() and we pass in the value 4, we would expect to see stairs with a length of 4 and a height of 4:

    X

    XX

    XXX

    XXXX

    ```{r}
    # You may feel more comfortable figuring this out in Python first, then translating into R later.
    mario_stairs <- function(num) {
      output <- ''
      for (i in 1:num) {
        for (j in 1:i) {
          output <- paste(output, 'X')
        }
        output <- gsub(' ','',output)
        print(output)
        output <- ''
      }
    }
    print(mario_stairs(4))
    ```
